\mytitle{}

### 2018-09-03 paper/paper.tex
Service theorem proof.

\usepackage[T1]{fontenc}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{bm}

@@

@@

@@

\Cref{fig:marl-granularity} shows that as more hosts are allocated to each learner, the fraction of traffic believed to be good (as observed at the server) decreases.
This manifests in two ways: the best-achievable performance decreases, as does the learning rate.
Given the UDP-like behaviour of Tcpreplay, being able to replicate the online performance of \citeauthor{DBLP:journals/eaai/MalialisK15} in the $n=2$ case suggests that the numeric simulation their work is entirely based upon does not capture the key interactions between TCP flows and packet drop as a control action.
From the findings of \cref{sec:tcp-multiplexing-and-fallback-behaviour} and the Mathis equation, their results should be considerably worse in practice.
%?? Expand according to the summary you posted in the notes document.
%That the use of UDP-like traffic replicates their experiments, compared against how real tcp behaves in mininet and according to the Mathis equation, shows that they really did not consider the behaviour of benign TCP in this environ (i.e., their results should be considerably worse in practice).

>>>>

\usepackage[T1]{fontenc}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}

@@

%thm environments
\newtheorem{thm}{Theorem}
\newtheorem{corr}{Corollary}[thm]

@@

\section{Threat Model}

?? The fine folks at most security conferences will want to see one. I suppose it serves its purpose by delineating what an attacker can/cannot do.

?? TODO: threat model.

@@

\Cref{fig:marl-granularity} shows that as more hosts are allocated to each learner, the fraction of traffic believed to be good (as observed at the server) decreases.
This manifests in two ways: the best-achievable performance decreases, as does the learning rate.
The first consequence arises analytically.
Given the probability that a host is legitimate, $P_G \in [0,1]$, it follows that a host will be malicious with probability $P_B = 1 - P_G$.
Defining \emph{imperfect service} to mean any case where all $n$ hosts connecting over a switch do not share the same classification (i.e., a mixture), then the probability that a switch is delivering imperfect service is $P_{M,n} = 1 - (P_G^2 - P_B^2)$.
\begin{thm}
	As $n$ increases, it is more likely that a switch will exhibit imperfect service, i.e., $\forall n \in \mathbb{Z}^{+}, P_{M,n} \le P_{M,n+1}$.
\end{thm}
\begin{proof}
	\emph{Base case:} $P_{M,1}=0, P_{M,2} = 1 - P_G^2 - P_B^2 > 0$.

	\emph{Inductive step:} Assume that the theorem holds for $n$. Observe that $P_G^n \ge P_G^{n+1}$ (resp.\ $P_B$). It then follows that:
	\begin{align*}
	P_G^n + P_B^n &\ge P_G^{n+1} + P_B^{n+1}\\
	1 - (P_G^n + P_B^n) &\le 1 - (P_G^{n+1} + P_B^{n+1})\\
	P_{M,n} &\le P_{M,n+1}
	\end{align*}
\end{proof}
\begin{corr}
	Restricting $P_G \in (0,1)$ so that both $P_G$ and $P_B$ are non-zero ensures strict inequality: $P_{M,n} < P_{M,n+1}$.
\end{corr}

Given the UDP-like behaviour of Tcpreplay, being able to replicate the online performance of \citeauthor{DBLP:journals/eaai/MalialisK15} in the $n=2$ case suggests that the numeric simulation their work is entirely based upon does not capture the key interactions between TCP flows and packet drop as a control action.
From the findings of \cref{sec:tcp-multiplexing-and-fallback-behaviour} and the Mathis equation, their results should be considerably worse in practice.
%?? Expand according to the summary you posted in the notes document.
%That the use of UDP-like traffic replicates their experiments, compared against how real tcp behaves in mininet and according to the Mathis equation, shows that they really did not consider the behaviour of benign TCP in this environ (i.e., their results should be considerably worse in practice).
